Subject-specific curves for time series forecasting of smart meter demand

### 2020-03-29 sscts-paper-1-wp.Rmd
Delete old section on autocorrelation in residuals

```{r one-day-ahead-forecast, fig.cap="(ref:one-day-ahead-forecast-cap)"}
model_df %>%
  filter(fcst_date == p_one_day_ahead_date) %>%
  unnest(cols = c(preds)) %>%
  # filter(bid %in% sample(unique(bid), 3),
  #        fcst_date %in% (dmy("13/3/2017")+0:4)) %>%
  filter(bid %in% sample(unique(bid), 6)) %>%
  mutate(ts = as_datetime(fcst_date) + minutes((period - 1) * 24 * 60 / 96)) %>%
  ggplot(aes(x = ts)) +
  geom_line(aes(y = wh), colour = "black", linetype = "dashed") +
  geom_line(aes(y = pred, colour = model), alpha = 0.7) +
  facet_wrap(~bid, ncol = 2, scales = "free_y") +
  labs(
    y = expression(Normalised ~ electricity ~ (Wh / m^2)),
    x = "Date",
    colour = "Model"
  ) +
  scale_x_datetime(date_labels = "%H:%M") +
  theme(legend.position = "bottom")
```

@@

<!-- ## Autocorrelation in residuals -->

<!-- __TODO: show a plot of ACF for SSCATTR residuals from several buildings based OR inspect the empirical autocorrelation function for the normalised residuals as recommended by Pinheiro and Bates, 1978.__ -->

<!-- __TODO:__ I don't think I should be comparing the out of sample residuals since each comes from a different model! Shouldn't I look at in-sample correlation? i.e. fit a model to some training data and then check in-sample ACF for residuals. Check how ACF is normally calculated in Rob/Shu papers (in sample or out of sample). -->

<!-- Here we examine if there is any remaining signal in the residuals of the SSCATTR model.  -->

<!-- __TODO:__ To do this we calculate the empirical autocorrelation function for the normalised residuals^[The normalised residuals are defined as $\mathbf{r}_i = \hat{\sigma}^{-1}(\hat{\Lambda}_i^{-\frac{1}{2}})^T(\mathbf{y}_i - \hat{\mathbf{y}}_i)$ where $\hat{\sigma}^2 \hat{\Lambda}_i$ is the estimated variance-covariance matrix for the within group errors.] [@Pinheiro1978-tg]. -->

<!-- ```{r} -->
<!-- bla <- model_df %>%  -->
<!--   filter(period == 70) %>%  -->
<!--   unnest(preds) %>%  -->
<!--   filter(bid == unique(bid)[3], -->
<!--          model == "SSCATTR") %>% -->
<!--   select(fcst_date, resid) %>%  -->
<!--   arrange(desc(fcst_date)) -->

<!-- acf(bla$resid, plot = FALSE)$acf %>%  -->
<!--   data.frame() %>%  -->
<!--   rename(Autocorrelation = ".") %>%  -->
<!--   rownames_to_column("lag") %>%  -->
<!--   mutate(lag = as.numeric(lag) - 1) %>%  -->
<!--   filter(lag != 0) %>%  -->
<!--   ggplot() + -->
<!--   geom_segment(aes(y = 0, yend = Autocorrelation, x = lag, xend = lag), -->
<!--                colour = ba_palette[1]) + -->
<!--   geom_point(aes(x = lag, y = Autocorrelation), colour = ba_palette[1]) + -->
<!--   geom_hline(yintercept = c(0.1, -0.1), linetype = "dashed", -->
<!--              colour = ba_palette[1]) + -->
<!--   labs(x = "Lag (days)", -->
<!--        y = "Autocorrelation") -->
<!-- ``` -->

>>>>

```{r one-day-ahead-forecast, fig.cap="(ref:one-day-ahead-forecast-cap)"}
model_df %>%
  filter(fcst_date == p_one_day_ahead_date) %>%
  unnest(cols = c(preds)) %>%
  # filter(bid %in% sample(unique(bid), 3),
  #        fcst_date %in% (dmy("13/3/2017")+0:4)) %>%
  filter(bid %in% sample(unique(bid), 6),
         model %in% c("Naive", "INS", "SSC")) %>%
  mutate(ts = as_datetime(fcst_date) + minutes((period - 1) * 24 * 60 / 96)) %>%
  ggplot(aes(x = ts)) +
  geom_line(aes(y = wh), colour = "black", linetype = "dashed") +
  geom_line(aes(y = pred, colour = model), alpha = 0.7) +
  facet_wrap(~bid, ncol = 2, scales = "free_y") +
  labs(
    y = expression(Normalised ~ electricity ~ (Wh / m^2)),
    x = "Date",
    colour = "Model"
  ) +
  scale_x_datetime(date_labels = "%H:%M") +
  theme(legend.position = "bottom")
```

@@
